\documentclass[bold]{deedy-resume-openfont}
\usepackage{fancyhdr}
 \usepackage{enumitem}
 \usepackage{fontawesome}
 \usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}
 
\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Shah}{Zaman}{ 
Android Developer\\
\href{mailto:shahzamanrai8@gmail.com}{\textbf{shahzamanrai8@gmail.com} |}
\href{tel:+923207913257}{\textbf{343 505 3916} |}
\href{https://github.com/ShahzamanRai/}{\textbf{Github} |}
\href{https://www.linkedin.com/in/shah-zaman-rai/}{\textbf{LinkedIn}}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Okara}
\descript{BS in Computer Science}
\location{Aug 2020 - Aug 2024 | Okara, PK}
\location{ CGPA: 3.34 / 4.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
\begin{itemize}[label=\textbullet, leftmargin=*, topsep=0pt, itemsep=-1ex]
    \item Software Engineering
    \item Operating Systems
    \item Databases
    \item Software Testing
    \item Software Requirement
    \item ICT
    \item Big Data Analysis
\end{itemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{\textbf{Android:}}
Android SDK \textbullet{} Kotlin \textbullet{} Java \\
Jetpack Compose \textbullet{} XML \textbullet{} Material 3  \\
Room Database \textbullet{} Dagger Hilt \textbullet{} Retrofit  \\
Clean Architecture \textbullet{} MVVM \textbullet{} Firebase  \\
\location{\textbf{Familiar:}}
Web \textbullet{} Python \textbullet{} C++ \textbullet{} C \textbullet{} Linux
\location{\textbf{Operating Systems:}}
Linux \textbullet{} Windows
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Interests
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Interests}
\begin{itemize}[leftmargin=0pt]
    \item \textbf{Mobile App Innovation:} Passionate about exploring new features and design patterns to create user-friendly and engaging mobile applications.
    \item \textbf{Health and Fitness:} Dedicate time to maintaining a healthy lifestyle through regular exercise and outdoor activities.
    \item \textbf{Exploring the Internet:} Curious about diverse online content, from tech forums to educational videos, to stay informed and inspired.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LANGUAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Languages}
\subsection{Proficiency}
\begin{itemize}[label=\textbullet, leftmargin=*, topsep=5pt, itemsep=-1ex]
    \item \textbf{English:} Conversational
    \item \textbf{Urdu:} Native
\end{itemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ABOUT ME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{About Me}
\runsubsection{Self-Taught Android Developer}
\descript{| \textbf{Seeking Opportunities}}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
    \item Initiated the development of immersive, user-centric Android apps with a strong passion for crafting engaging and innovative applications.
    \item Specialized in \textbf{Jetpack Compose} and \textbf{Kotlin}, specializing in captivating and functional designs.
    \item Expertise in seamless integration of \textbf{Database} and \textbf{API} for optimal performance.
    \item Dedicated to continuous learning, Android trends, and leveraging Linux as my primary platform to fuel innovative app development.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{PROJECTS / OPEN-SOURCE}

\runsubsection{\href{https://github.com/ShahzamanRai/Music_player}{Music Player App \faLink}}
\descript{| \textbf{Kotlin/XML}}
\begin{tightemize}
    \item Led the creation of an Offline Music Player App utilizing \textbf{Kotlin} and \textbf{XML}, strategically prioritizing the implementation of seamless playback controls and optimizing playlist management efficiency. Leveraged the \textbf{Glide} library for efficient image loading and rendering to enhance the user experience.
    \item Demonstrated advanced skills in UI design and proficient app development.
    \item Engineered intuitive user interface for enhanced user experience.
\end{tightemize}
\sectionsep

\runsubsection{\href{https://github.com/ShahzamanRai/Dev_Docs}{Dev Docs App \faLink}}
\descript{| \textbf{Kotlin/Jetpack Compose}}
\begin{tightemize}
    \item Designed and developed a user-friendly Dev Docs application using \textbf{Kotlin} and \textbf{Jetpack Compose}, seamlessly integrating \textbf{Web-View} with \textbf{Material 3} design principles. This project served as a dynamic platform to gain hands-on expertise in \textbf{Jetpack Compose} while developing a user-friendly resource for accessing development documentation.
    \item Created a user-friendly resource for developers to access and explore development documentation.
    \item Seamlessly integrated \textbf{Web-View} functionality to enable access to external documentation
    \item Aligned app design with \textbf{Material 3} principles for a modern and intuitive user experience.
\end{tightemize}
\sectionsep

\runsubsection{\href{https://github.com/ShahzamanRai/Weather_Application}{Weather App \faLink}}
\descript{| \textbf{Kotlin/Jetpack Compose}}
\begin{tightemize}
    \item Engineered a visually captivating Weather Application utilizing \textbf{Kotlin}, \textbf{Jetpack Compose}, and \textbf{Clean Architecture} principles. This project not only provided an immersive experience in \textbf{Clean Architecture} but also showcased proficiency in \textbf{Jetpack Compose} and dependency injection using \textbf{Dagger Hilt}, resulting in a polished user interface for accessing weather data.
    \item Implemented \textbf{Clean Architecture} principles to ensure a modular and maintainable codebase.
    \item Demonstrated advanced skills in \textbf{Jetpack Compose} to create a polished and dynamic user interface.
    \item Strengthened understanding of architectural patterns, modern UI frameworks, and \textbf{dependency injection} through project completion.
\end{tightemize}
\sectionsep


\end{minipage} 
\end{document}  \documentclass[]{article}
